\section*{Changelog and To-do list}
\subsection*{Changelog}
\begin{itemize}
    \item v0.1: First version of doc for CDS.
    \item v0.2: Updated version. Filling in sections to document work done to-date.
    \begin{itemize}
        \item \textbf{Introduction} provided more specific context for the Run 3 analysis. 

        \item \textbf{Section 3 Object Definitions and Event Selection}: added up-to-date Run3 object descriptions and their references.
        
        \item \textbf{Section 5 Signal and Background modelling}: replaced initial spurious signal studies with a much more advanced study, including proper background decomposition, GPR smoothing and low-stats categories treatment
        
        \item \textbf{Section 6 Background Estimation}: added results for all differential categories.
        
        \item \textbf{Section 7 Uncertainties}: added descriptions of experimental uncertainties. Theoretical uncertainties are still to be evaluated.
        
        \item \textbf{Section 9 Signal Yield Extraction}: added more detailed descriptions to improve clarity.
        
        \item \textbf{Section 12 Conclusion} added a preliminary conclusion paragraph, to be updated once results are finalised.
        
        \item \textbf{New appendices}: Background Templates, Data Sidebands for Wald tests, Truth Isolation Studies. 
    \end{itemize}
\end{itemize}

\section*{Publication timeline}

\begin{table}[h]
    \centering
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Date} & \textbf{Event}  \\
        \hline
        2025/08/05 & EB request \\
        2025/10/24 & All studies to-date updated in INT note \\
        2026/02 & Publication target (Moriond) \\
        \hline
    \end{tabular}
    \caption{Analysis timeline, as of October 2025.}
\end{table}


%\listoftodos
\section*{To-do list (Status October 2025)}

Main analysis TO-DO items: 
 \begin{itemize}
    \item Cross-checks with new product cuts; if successful, product cuts will
    be adopted for the analysis

    \item Theoretical uncertainties 

    \item Implement fix for timing-cut in isolation calculation. Recompute background.
\end{itemize}
Other TO-DO items:
    \begin{itemize}
    \item Unfolding using matrix-inversion instead of bin-by-bin correction factors.

    \item Full systematic uncertainties to replace simplified scheme.

    \item Analysis CP task, currently $\sim$ 1/3 complete (\href{https://its.cern.ch/jira/browse/ATLASEG-426}{link to JIRA ticket}).
 
\end{itemize}



 
\clearpage
